A Two-Infall Star Formation History with Outflows and Radial Migration

### 2025-02-19 src/tex/ms.tex
Updates from Overleaf

% Author list
\author[0000-0003-3781-0747]{Liam O.\ Dubay}
\affiliation{\osuaffil}
\affiliation{\ccappaffil}
\author[0000-0001-7258-1834]{Jennifer A.\ Johnson}
\affiliation{\osuaffil}
\affiliation{\ccappaffil}
\author[0000-0002-6534-8783]{James W.\ Johnson}
\affiliation{Observatories of the Carnegie Institution for Science, 813 Santa Barbara St., Pasadena CA 91101, USA}
\affiliation{\osuaffil}
\affiliation{\ccappaffil}
\author[0000-0002-2854-5796]{John D. Roberts}
\affiliation{\osuaffil}
\affiliation{\ccappaffil}
% \author[0000-0001-7775-7261]{David H. Weinberg}
\author{coauthors}

@@

\begin{abstract}
    Abstract.
\end{abstract}

\section{Outline}
\input{outline.tex}

@@

@@

We obtain a sample of \num{171635} red giant branch and red clump stars with high-quality spectra using the selection criteria listed in Table \ref{tab:sample}, which are adapted from \citet{hayden_chemical_2015}. Table \ref{tab:uncertainties} presents the median statistical uncertainty and uncertainty dispersion ($95^{\rm th} - 5^{\rm th}$ percentile difference) of the calibrated [Fe/H] and [O/Fe] abundances for our sample. We use the \citet{bailer-jones_estimating_2021} photo-geometric distance estimates from {\it Gaia} Early Data Release 3 \citep{gaia_collaboration_gaia_2016,gaia_collaboration_gaia_2021} included in the APOGEE DR17 catalog. When calculating the galactocentric radius $R_{\rm gal}$ and midplane distance $z$ of each star, we assume the distance between the Sun and the Galactic center is $R_\odot=8.122\,{\rm kpc}$ \citep{gravity_collaboration_detection_2018} and the Solar midplane distance is $z_\odot=20.8\,{\rm pc}$ \citep{bennett_vertical_2019}. Table \ref{tab:apogee-regions} presents the number of APOGEE stars in bins of $R_{\rm gal}$ and $|z|$; typical distance uncertainties are much smaller than the bin width.

@@

Our second age catalog uses the [C/N]--age relation for red giant branch and red clump stars. 
\todo{Paragraph describing [C/N]-derived ages (get help from Jack).}
This method has the benefit of providing age estimates for luminous giants, which increases the sample size at farther distances from the Sun. However, systematic effects of the [C/N]--age relation mean that these ages are most trustworthy in the range $1\sim10$ Gyr. We estimate ages for \num{113464} stars across the disk, including \num{20995} in the Solar neighborhood.

@@

\begin{figure*}
    \centering
    \includegraphics{figures/onezone_params.pdf}
    \caption{Gas abundance tracks in the [O/Fe]--[Fe/H] plane for one-zone chemical evolution models which assume different values for the infall history parameters. In each panel, one parameter is varied according to the legend while the other two are held fixed. The open symbols along each curve mark logarithmic steps in time, as denoted in panel (b). The marginal panels show the corresponding stellar abundance distributions, which are convolved with a Gaussian kernel with a width of 0.02 dex for visual clarity. All models use the {\tt yZ1} yield set and assume $\eta=0.4$.}
    \label{fig:twoinfall-parameters}
\end{figure*}

@@

Figure \ref{fig:mdf-evolution} shows that even with pre-enriched infall, both of our models predict that the MDF shifts to the left going from younger to older populations. On the other hand, the data show that the MDF broadens with age, which we attribute to radial migration, but its peak does not shift substantially over the past $\sim6-8$ Gyr. While the mode of the MDF shifts depending on the radial bin, its evolution is remarkably consistent over the entire disk, in line with the equilibrium scenario of \citet{johnson_milky_2024}.

@@

\software{\vice \citep{johnson_impact_2020}, Astropy \citep{astropy_collaboration_astropy_2013,astropy_collaboration_astropy_2018,astropy_collaboration_astropy_2022}, scikit-learn \citep{pedregosa_scikit-learn_2011}, SciPy \citep{virtanen_scipy_2020}, Matplotlib \citep{hunter_matplotlib_2007}}

>>>>

% Author list
\author[0000-0003-3781-0747]{Liam O.\ Dubay}
\affiliation{\osuaffil}
\affiliation{\ccappaffil}
\author[0000-0001-7258-1834]{Jennifer A.\ Johnson}
\affiliation{\osuaffil}
\affiliation{\ccappaffil}
\author[0000-0002-6534-8783]{James W.\ Johnson}
\affiliation{Observatories of the Carnegie Institution for Science, 813 Santa Barbara St., Pasadena CA 91101, USA}
% \affiliation{\osuaffil}
% \affiliation{\ccappaffil}
\author[0000-0002-2854-5796]{John D.\ Roberts}
\affiliation{\osuaffil}
\affiliation{\ccappaffil}
% \author[0000-0001-7775-7261]{David H. Weinberg}
\author{coauthors}

@@

\begin{abstract}
    % The Milky Way's stellar disk can be separated into multiple chemically and kinematically distinct components. 
    The two-infall model has long been proposed to explain the formation of the Milky Way's thick and thin disks through two consecutive gas accretion epochs. It has successfully reproduced observed abundance patterns in the Solar neighborhood and across the disk. However, few studies have explored a two-infall with significant mass-loaded outflows
\end{abstract}

% \section{Outline}
% \input{outline.tex}

@@

\citet{palla_mgfe_2022} test prescriptions for radial migration but assume that it does not affect supernova enrichment (i.e., that most supernovae explode near the star's birthplace).

@@

We obtain a sample of \num{171635} red giant branch and red clump stars with high-quality spectra using the selection criteria listed in Table \ref{tab:sample}, which are adapted from \citet{hayden_chemical_2015}. Table \ref{tab:uncertainties} presents the median statistical uncertainty and uncertainty dispersion ($95^{\rm th} - 5^{\rm th}$ percentile difference) of the calibrated [Fe/H] and [O/Fe] abundances for our sample. When calculating the galactocentric radius $R_{\rm gal}$ and midplane distance $z$ of each star, we use the \citet{bailer-jones_estimating_2021} photo-geometric distance estimates from {\it Gaia} Early Data Release 3 \citep{gaia_collaboration_gaia_2016,gaia_collaboration_gaia_2021} included in the APOGEE DR17 catalog and we adopt the Galactic coordinates of the Sun $(R,z)_\odot=(8.122, 0.0208)\,{\rm kpc}$ \citep{gravity_collaboration_detection_2018,bennett_vertical_2019}. Table \ref{tab:apogee-regions} presents the number of APOGEE stars in bins of $R_{\rm gal}$ and $|z|$; typical distance uncertainties are much smaller than the bin width.

@@

Our second age catalog uses the [C/N]--age relation for red giant branch and red clump stars. 
\todo{Paragraph describing [C/N]-derived ages (get help from Jack).}
This method has the benefit of providing age estimates for luminous giants, which increases the sample size at farther distances from the Sun. However, systematic effects of the [C/N]--age relation mean that these ages are most trustworthy in the range $1\sim10$ Gyr. We estimate ages for \num{113464} stars across the disk, including \num{20995} in the Solar neighborhood.
\todo{Note about metallicity cutoff for luminous giants.}

@@

\begin{figure*}
    \centering
    \includegraphics{figures/onezone_params.pdf}
    \caption{Gas abundance tracks in the [O/Fe]--[Fe/H] plane for one-zone chemical evolution models which assume different values for the infall history parameters. In each panel, one parameter is varied according to the legend while the other two are held fixed. The open symbols along each curve mark logarithmic steps in time, as denoted in panel (b). The marginal panels show the corresponding stellar abundance distributions, which are convolved with a Gaussian kernel with a width of 0.02 dex for visual clarity. All models use the {\tt yZ1} yield set and assume $\eta=0.2$.}
    \label{fig:twoinfall-parameters}
\end{figure*}

@@

Figure \ref{fig:mdf-evolution} shows that even with pre-enriched infall, both of our models predict that the MDF shifts to the left going from younger to older populations. On the other hand, the data show that the MDF broadens with age, which we attribute to radial migration, but its peak does not shift substantially over the past $\sim6-8$ Gyr. While the mode of the MDF shifts depending on the radial bin, its evolution is remarkably consistent over the entire disk, in line with the equilibrium scenario of \citet{johnson_milky_2024}.
\todo{Note about metallicity cutoff for luminous giants.}

@@

\software{\vice \citep{johnson_impact_2020}, Astropy \citep{astropy_collaboration_astropy_2013,astropy_collaboration_astropy_2018,astropy_collaboration_astropy_2022}, scikit-learn \citep{pedregosa_scikit-learn_2011}, SciPy \citep{virtanen_scipy_2020}, Matplotlib \citep{hunter_matplotlib_2007}.}
